---
title: "Differential Expression Analysis"
author: "Paul Marcoux"
date: today
date-format: "16 02 2026"
format: 
  html:
    page-layout: full
    toc: true
    toc-depth: 3
    toc-location: left
    code-fold: true
    code-summary: "Show code"
    code-tools: true
    theme: cosmo
    embed-resources: true
    number-sections: true
execute:
  warning: false
  message: false
  fig-width: 12
  column: page
params:
  min_expression: 0.05
  threshold_pvalue: 0.05
  threshold_FC: 0.5
  n_top_genes: 15
---

```{r}
#| warning: false
#| label: setup
library(here)
library(DT)
source(here("src/Metadata.R"))
source(here("src/DE_analysis.R"))

# Extraire les paramètres
min_expression <- params$min_expression
threshold_pvalue <- params$threshold_pvalue
threshold_FC <- params$threshold_FC
n_top_genes <- params$n_top_genes
```

**Analysis parameters:**

-   Minimum expression threshold: `r params$min_expression`
-   p-value threshold (BH corrected): `r params$threshold_pvalue`
-   Log2 fold-change threshold: ±`r params$threshold_FC`
-   Top genes displayed: `r params$n_top_genes`

```{r}
#| label: helper-function
#| include: false

analyze_pathway <- function(file_path, title) {
  data_FC <- import(file_path)
  data_FC_filter <- open_filter(data_FC, min_expression, threshold_pvalue, threshold_FC)
  data_FC_filter <- labels_n_up_down(data_FC_filter, n = 10)
  
  data_FC_up <- top_n_upregulated(data_FC_filter, n = 15)
  data_FC_down <- top_n_downregulated(data_FC_filter, n = 15)
  data_FC_up_down <- rbind(data_FC_up, data_FC_down)
  
  # Afficher les plots
  print(Plot_DE_up_down(data_FC_up_down, title))
  print(Plot_volcano_DE(data_FC_filter, title))
  
  # Retourner les données filtrées pour analyses ultérieures
  invisible(data_FC_filter)
}
```

## Cluster 15 vs All

### Reactome
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_All_wo_cluster15/2024-02_Reactome_Exp_AllSample_cluster_15_vs_All_wo_cluster15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Reactome Cluster 15 vs All")
Plot_volcano_DE(data_FC_filter,"Reactome Cluster 15 vs All")

```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Biocarta
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_All_wo_cluster15/Biocarta_Exp_AllSample_cluster_15_vs_All_wo_cluster15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Biocarta Cluster 15 vs All")
Plot_volcano_DE(data_FC_filter,"Biocarta Cluster 15 vs All")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
> *"We present preclinical studies demonstrating that treatment with CD19-specific, chimeric antigen receptor (CAR)–modified T cells that are further modified to constitutively secrete IL-12 are able to safely eradicate established disease in the absence of prior conditioning. We demonstrate in a novel syngeneic tumor model that tumor elimination requires both CD4^+^ and CD8^+^ T-cell subsets, autocrine IL-12 stimulation, and subsequent IFNγ secretion by the CAR^+^ T cells. Importantly, IL-12–secreting, tumor-targeted T cells acquire intrinsic resistance to T regulatory cell–mediated inhibition. Based on these preclinical data, we anticipate that adoptive therapy using CAR-targeted T cells modified to secrete IL-12 will obviate or reduce the need for potentially hazardous conditioning regimens to achieve optimal antitumor responses in cancer patients."*

[Hollie J. Pegram et al, Immunobiology 2012](https://ashpublications.org/blood/article/119/18/4133/30054/Tumor-targeted-T-cells-modified-to-secrete-IL-12)

### C5
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_All_wo_cluster15/C5_Exp_AllSample_cluster_15_vs_All_wo_cluster15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"C5 Cluster 15 vs All")
Plot_volcano_DE(data_FC_filter,"C5 Cluster 15 vs All")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::

### Gene Expression
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_All_wo_cluster15/Exp_AllSample_cluster_15_vs_All_wo_cluster15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Gene Expression Cluster 15 vs All")
Plot_volcano_DE(data_FC_filter,"Gene Expression Cluster 15 vs All")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::

XCL1 is a small cytokine belonging to the C chemokine family produced primarily by activated CD8+ T cells and natural killer (NK) cells.
XCL 2 is predominantly expressed in activated T cells, but can also be found at low levels in unstimulated cells.


### Hallmark
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_All_wo_cluster15/H_Exp_AllSample_cluster_15_vs_All_wo_cluster15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Hallmark Cluster 15 vs All")
Plot_volcano_DE(data_FC_filter,"Hallmark Cluster 15 vs All")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::

### Wikipathway
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_All_wo_cluster15/WikiPathway_2021_Human_Exp_AllSample_cluster_15_vs_All_wo_cluster15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Wikipathway Cluster 15 vs All")
Plot_volcano_DE(data_FC_filter,"Wikipathway Cluster 15 vs All")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::

## CAR-T cluster 15 vs No-CAR-T cluster 15

### Reactome
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/CART_cluster_15_vs_noCART_cluster_15/2024-02_Reactome_Exp_AllSample_CART_cluster_15_vs_noCART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Reactome CAR-T vs No-CAR-T")
Plot_volcano_DE(data_FC_filter,"Reactome CAR-T vs No-CAR-T")

```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Biocarta
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/CART_cluster_15_vs_noCART_cluster_15/Biocarta_Exp_AllSample_CART_cluster_15_vs_noCART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Biocarta CAR-T vs No-CAR-T")
Plot_volcano_DE(data_FC_filter,"Biocarta CAR-T vs No-CAR-T")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
Multiple signaling modules linked to T-cell receptor engagement and downstream regulation :

-   TCRA : Lck and Fyn tyrosine kinases in initiation of TCR Activation

-   CSK : Activation of Csk by cAMP-dependent Protein Kinase Inhibits Signaling through the T Cell Receptor

-   TOB1 : Role of Tob in T-cell activation

-   TCYTOTOXIC : T Cytotoxic Cell Surface Molecules

-   NO2IL12 : NO2-dependent IL 12 Pathway in NK cells

-   

### C5
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/CART_cluster_15_vs_noCART_cluster_15/C5_Exp_AllSample_CART_cluster_15_vs_noCART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"C5 CAR-T vs No-CAR-T")
Plot_volcano_DE(data_FC_filter,"C5 CAR-T vs No-CAR-T")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Gene Expression
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/CART_cluster_15_vs_noCART_cluster_15/Exp_AllSample_CART_cluster_15_vs_noCART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Gene Expression CAR-T vs No-CAR-T")
Plot_volcano_DE(data_FC_filter,"Gene Expression CAR-T vs No-CAR-T")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Hallmark
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/CART_cluster_15_vs_noCART_cluster_15/H_Exp_AllSample_CART_cluster_15_vs_noCART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Hallmark CAR-T vs No-CAR-T")
Plot_volcano_DE(data_FC_filter,"Hallmark CAR-T vs No-CAR-T")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Wikipathway
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/CART_cluster_15_vs_noCART_cluster_15/WikiPathway_2021_Human_Exp_AllSample_CART_cluster_15_vs_noCART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Wikipathway CAR-T vs No-CAR-T")
Plot_volcano_DE(data_FC_filter,"Wikipathway CAR-T vs No-CAR-T")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
## Cluster 15 vs Cluster 6

### Reactome
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_cluster_6/2024-02_Reactome_Exp_AllSample_cluster_15_vs_cluster_6.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Reactome Cluster 15 vs cluster 6")
Plot_volcano_DE(data_FC_filter,"Reactome Cluster 15 vs cluster 6")

```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Biocarta
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_cluster_6/Biocarta_Exp_AllSample_cluster_15_vs_cluster_6.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Biocarta Cluster 15 vs cluster 6")
Plot_volcano_DE(data_FC_filter,"Biocarta Cluster 15 vs cluster 6")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
-   HSWI_SNF : Chromatin Remodeling by hSWI/SNF ATP-dependent Complexes

-   BARD1 : BRCA1-dependent Ub-ligase activity

-   MCM : CDK Regulation of DNA Replication

-   PTC1 : Sonic Hedgehog (SHH) Receptor Ptc1 Regulates cell cycle

### C5
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_cluster_6/C5_Exp_AllSample_cluster_15_vs_cluster_6.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"C5 Cluster 15 vs cluster 6")
Plot_volcano_DE(data_FC_filter,"C5 Cluster 15 vs cluster 6")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Gene Expression
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_cluster_6/Exp_AllSample_cluster_15_vs_cluster_6.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Gene Expression Cluster 15 vs cluster 6")
Plot_volcano_DE(data_FC_filter,"Gene Expression Cluster 15 vs cluster 6")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Hallmark
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_cluster_6/H_Exp_AllSample_cluster_15_vs_cluster_6.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Hallmark Cluster 15 vs cluster 6")
Plot_volcano_DE(data_FC_filter,"Hallmark Cluster 15 vs cluster 6")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
-   HALLMARK_IL6_JAK_STAT3_SIGNALING : **intense cytokine-driven inflammatory signaling**.

-   Mitotic Spindle : Cell division

### Wikipathway
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Cluster_15_vs_cluster_6/WikiPathway_2021_Human_Exp_AllSample_cluster_15_vs_cluster_6.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Wikipathway Cluster 15 vs cluster 6")
Plot_volcano_DE(data_FC_filter,"Wikipathway Cluster 15 vs cluster 6")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
## DLBCL cluster 15 vs LN cluster 15

### Reactome
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/DLBCL_cluster_15_vs_LN_cluster_15/2024-02_Reactome_Exp_AllSample_DLBCL_cluster_15_vs_LN_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Reactome DLBCL cluster 15 vs LN cluster_15")
Plot_volcano_DE(data_FC_filter,"Reactome DLBCL cluster 15 vs LN cluster_15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Biocarta
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/DLBCL_cluster_15_vs_LN_cluster_15/Biocarta_Exp_AllSample_DLBCL_cluster_15_vs_LN_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Biocarta DLBCL cluster 15 vs LN cluster_15")
Plot_volcano_DE(data_FC_filter,"Biocarta DLBCL cluster 15 vs LN cluster_15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
SET : Granzyme A mediated Apoptosis Pathway

### C5
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/DLBCL_cluster_15_vs_LN_cluster_15/C5_Exp_AllSample_DLBCL_cluster_15_vs_LN_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"C5 DLBCL cluster 15 vs LN cluster_15")
Plot_volcano_DE(data_FC_filter,"C5 DLBCL cluster 15 vs LN cluster_15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Gene Expression
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/DLBCL_cluster_15_vs_LN_cluster_15/Exp_AllSample_DLBCL_cluster_15_vs_LN_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Gene Expression DLBCL cluster 15 vs LN cluster_15")
Plot_volcano_DE(data_FC_filter,"Gene Expression DLBCL cluster 15 vs LN cluster_15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Hallmark
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/DLBCL_cluster_15_vs_LN_cluster_15/H_Exp_AllSample_DLBCL_cluster_15_vs_LN_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Hallmark DLBCL cluster 15 vs LN cluster_15")
Plot_volcano_DE(data_FC_filter,"Hallmark DLBCL cluster 15 vs LN cluster_15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Wikipathway
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/DLBCL_cluster_15_vs_LN_cluster_15/WikiPathway_2021_Human_Exp_AllSample_DLBCL_cluster_15_vs_LN_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Wikipathway DLBCL cluster 15 vs LN cluster_15")
Plot_volcano_DE(data_FC_filter,"Wikipathway DLBCL cluster 15 vs LN cluster_15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
## Post Car-T Cluster 15 vs pre-CAR-T cluster 15

### Reactome
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Post_CART_cluster_15_pre_CART_cluster_15/2024-02_Reactome_Exp_AllSample_post_CART_cluster_15_vs_pre_CART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Reactome Post Car-T cluster 15 vs pre-Car-T cluster 15")
Plot_volcano_DE(data_FC_filter,"Reactome Post Car-T cluster 15 vs pre-Car-T cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Biocarta
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Post_CART_cluster_15_pre_CART_cluster_15/Biocarta_Exp_AllSample_post_CART_cluster_15_vs_pre_CART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Biocarta Post Car-T cluster 15 vs pre-Car-T cluster 15")
Plot_volcano_DE(data_FC_filter,"Biocarta Post Car-T cluster 15 vs pre-Car-T cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### C5
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Post_CART_cluster_15_pre_CART_cluster_15/C5_Exp_AllSample_post_CART_cluster_15_vs_pre_CART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"C5 Post Car-T cluster 15 vs pre-Car-T cluster 15")
Plot_volcano_DE(data_FC_filter,"C5 Post Car-T cluster 15 vs pre-Car-T cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Gene Expression
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Post_CART_cluster_15_pre_CART_cluster_15/Exp_AllSample_post_CART_cluster_15_vs_pre_CART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Gene Expression Post Car-T cluster 15 vs pre-Car-T cluster 15")
Plot_volcano_DE(data_FC_filter,"Gene Expression Post Car-T cluster 15 vs pre-Car-T cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Hallmark
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Post_CART_cluster_15_pre_CART_cluster_15/H_Exp_AllSample_post_CART_cluster_15_vs_pre_CART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Hallmark Post Car-T cluster 15 vs pre-Car-T cluster 15")
Plot_volcano_DE(data_FC_filter,"Hallmark Post Car-T cluster 15 vs pre-Car-T cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Wikipathway
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Post_CART_cluster_15_pre_CART_cluster_15/WikiPathway_2021_Human_Exp_AllSample_post_CART_cluster_15_vs_pre_CART_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Wikipathway Post Car-T cluster 15 vs pre-Car-T cluster 15")
Plot_volcano_DE(data_FC_filter,"Wikipathway Post Car-T cluster 15 vs pre-Car-T cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
## Relapse Cluster 15 vs Diag Cluster 15

### Reactome
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Relapse_cluster_15_vs_diag_cluster_15/2024-02_Reactome_Exp_AllSample_relapse_cluster_15_vs_diag_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Reactome Relapse Cluster 15 vs Diag Cluster 15")
Plot_volcano_DE(data_FC_filter,"Reactome Relapse Cluster 15 vs Diag Cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Biocarta
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Relapse_cluster_15_vs_diag_cluster_15/Biocarta_Exp_AllSample_relapse_cluster_15_vs_diag_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Biocarta Relapse Cluster 15 vs Diag Cluster 15")
Plot_volcano_DE(data_FC_filter,"Biocarta Relapse Cluster 15 vs Diag Cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### C5
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Relapse_cluster_15_vs_diag_cluster_15/C5_Exp_AllSample_relapse_cluster_15_vs_diag_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"C5 Relapse Cluster 15 vs Diag Cluster 15")
Plot_volcano_DE(data_FC_filter,"C5 Relapse Cluster 15 vs Diag Cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Gene Expression
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Relapse_cluster_15_vs_diag_cluster_15/Exp_AllSample_relapse_cluster_15_vs_diag_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Gene Expression Relapse Cluster 15 vs Diag Cluster 15")
Plot_volcano_DE(data_FC_filter,"Gene Expression Relapse Cluster 15 vs Diag Cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Hallmark
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Relapse_cluster_15_vs_diag_cluster_15/H_Exp_AllSample_relapse_cluster_15_vs_diag_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Hallmark Relapse Cluster 15 vs Diag Cluster 15")
Plot_volcano_DE(data_FC_filter,"Hallmark Relapse Cluster 15 vs Diag Cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::
### Wikipathway
::: panel-tabset
#### Plots
```{r}
#| echo: false
#| warning: false
data_FC <- import(here("data/Signature_scores/Relapse_cluster_15_vs_diag_cluster_15/WikiPathway_2021_Human_Exp_AllSample_relapse_cluster_15_vs_diag_cluster_15.csv")) 
data_FC_filter <- open_filter(data_FC,min_expression,threshold_pvalue,threshold_FC)
data_FC_filter <- labels_n_up_down(data_FC_filter,n=10)

data_FC_15_upregulated <- top_n_upregulated(data_FC_filter,n=15)
data_FC_15_downregulated <- top_n_downregulated(data_FC_filter,n=15)

data_FC_up_down <- rbind(data_FC_15_upregulated,data_FC_15_downregulated)

Plot_DE_up_down(data_FC_up_down,"Wikipathway Relapse Cluster 15 vs Diag Cluster 15")
Plot_volcano_DE(data_FC_filter,"Wikipathway Relapse Cluster 15 vs Diag Cluster 15")
```
#### Data Table

```{r}
#| echo: false
datatable(
  data_FC_filter,
  options = list(pageLength = 15, scrollX = TRUE),
  filter = 'top'
)
```
:::